Optimal Symmetric Multimodal Templates and Concatenated Random Forests for Supervised Brain Tumor Segmentation (Simplified) with \textit{ANTsR}

### 2014-05-03 paper.tex

\begin{abstract} 
Automated brain tumor segmentation in MRI is complicated by the lack
of prior knowledge concerning tumor location, spatial extent, shape,
possible displacement of normal tissue, and intensity signature.
%These factors limit the applicability of techniques with established
%performance in related tasks such as normal brain tissue
%segmentation.  
To accommodate such complications, we introduce a framework for supervised
segmentation based on multiple modality intensity, geometry, and asymmetry feature sets.  These features drive a supervised whole-brain and tumor segmentation
approach based on random forest-derived probabilities.  The
asymmetry-related features (based on optimal symmetric multimodal 
templates) demonstrate excellent discriminative 
properties within this framework. We also gain performance by  
generating probability maps from random forest models and using these maps 
for a refining Markov random field regularized probabilistic segmentation.  
This strategy allows us to interface the supervised learning capabilities 
of the random forest model with regularized probabilistic segmentation
using the recently developed \textit{ANTsR} 
package---a comprehensive statistical and visualization interface between the
popular Advanced Normalization Tools (ANTs) and the \textit{R}
statistical project. 
%\textit{ANTsR} integrates proven image analysis methods
%for image registration, segmentation, bias correction, and
%template building with \textit{R}'s statistical and machine
%learning techniques and state-of-the-art visualization possibilities.  
The reported algorithmic framework was the
top-performing entry in the MICCAI 2013 Multimodal Brain Tumor
Segmentation challenge.  The challenge data were widely varying 
consisting of both high-grade and low-grade glioma tumor 
four-modality MRI from five different institutions.
Average Dice overlap measures for the final algorithmic assessment
were 0.87, 0.78, and 0.74 for ``complete'', ``core'', and ``enhanced'' 
tumor components, respectively.
%and, to our knowledge, is the only entry for
%both challenge years (2012 \& 2013) which has been made publicly
%available.
\end{abstract}

>>>>

\begin{abstract} 
Segmenting and quantifying gliomas from MRI is an important task for diagnosis, planning intervention, 
and for tracking tumor changes over time.
However, this task is complicated by the lack
of prior knowledge concerning tumor location, spatial extent, shape,
possible displacement of normal tissue, and intensity signature.
%These factors limit the applicability of techniques with established
%performance in related tasks such as normal brain tissue
%segmentation.  
To accommodate such complications, we introduce a framework for supervised
segmentation based on multiple modality intensity, geometry, and asymmetry feature sets.  These features drive a supervised whole-brain and tumor segmentation
approach based on random forest-derived probabilities.  The
asymmetry-related features (based on optimal symmetric multimodal 
templates) demonstrate excellent discriminative 
properties within this framework. We also gain performance by  
generating probability maps from random forest models and using these maps 
for a refining Markov random field regularized probabilistic segmentation.  
This strategy allows us to interface the supervised learning capabilities 
of the random forest model with regularized probabilistic segmentation
using the recently developed \textit{ANTsR} 
package---a comprehensive statistical and visualization interface between the
popular Advanced Normalization Tools (ANTs) and the \textit{R}
statistical project. 
%\textit{ANTsR} integrates proven image analysis methods
%for image registration, segmentation, bias correction, and
%template building with \textit{R}'s statistical and machine
%learning techniques and state-of-the-art visualization possibilities.  
The reported algorithmic framework was the
top-performing entry in the MICCAI 2013 Multimodal Brain Tumor
Segmentation challenge.  The challenge data were widely varying 
consisting of both high-grade and low-grade glioma tumor 
four-modality MRI from five different institutions.
Average Dice overlap measures for the final algorithmic assessment
were 0.87, 0.78, and 0.74 for ``complete'', ``core'', and ``enhanced'' 
tumor components, respectively.
%and, to our knowledge, is the only entry for
%both challenge years (2012 \& 2013) which has been made publicly
%available.
\end{abstract}
